### 2021-07-05 rad-icfp-2021/purerad.tex
finishing to erase shift1

    \begin{tabular}{c l}
        &$\directD{\rho}{\Gamma}{Y}$(!prod(A)!) \\
        =& !let x,Y$_{1}$= <0, fun (X,z) -> Y(X)> in! \\
        & !let B,Y$_{2}$= <A, fun (X,x,Z) -> Y(X+Z,x)> in!\\
        & !let A$_{0}$= scanl * x B in!\\
        & !let A$_{1}$= map2 (a,b.b) A$_{0}$ B in!\\
        & !let A$_{2}$= shift1 (map2 (a,b.a) A$_{0}$ B) in!\\
        & !let A$_{3}$= scanr * 1 A$_{1}$ in!\\
        & !<prod(B), fun (X,z) -> Y$_{2}$(X,0,map2 (a,b. a*z*b) A$_{2}$ A$_{3}$)>! 
    \end{tabular}
\end{example}

@@

\begin{tabular}{{r c l}}
    $\nabla_A$!prod(A)! &=& !map2 * (scanr * 1 A) (shift1(scanl * 1 A))!\\
    $\nabla_A$!sum(A)! &=& !map (x -> 1) A!\\
    $\nabla_A$!dot(A,B)! &=& !B! 
\end{tabular}
\end{example}

>>>>

    \begin{tabular}{c l}
        &$\directD{\rho}{\Gamma}{Y}$(!prod(A)!) \\
        =& !let y,Y$_{1}$= <0, fun (X,z) -> Y(X)> in! \\
        & !let B,Y$_{2}$= <A, fun (X,x,Z) -> Y(X+Z,x)> in!\\
        & !let A$_{0}$= shift1R (scanl * y B) in!\\
        & !let A$_{1}$= shift1L (map2 (a,b.b) A$_{0}$ B) in!\\
        & !let A$_{2}$= map2 (a,b.a) A$_{0}$ B in!\\
        & !let A$_{3}$= scanr * 1 A$_{1}$ in!\\
        & !<prod(B), fun (X,z) -> Y$_{2}$(X,0,map2 (a,b. a*z*b) A$_{2}$ A$_{3}$)>! 
    \end{tabular}
\end{example}

@@

\begin{tabular}{{r c l}}
    $\nabla_A$!prod(A)! &=& !map2 * (scanr * 1 (shift1L A)) (shift1R (scanl * 1 A))!\\
    $\nabla_A$!sum(A)! &=& !map (x -> 1) A!\\
    $\nabla_A$!dot(A,B)! &=& !B! 
\end{tabular}
\end{example}
